Meta-analysis

### 2020-05-29 04_MetaAnalysis.Rmd
added pval plot

```
```{r}
dat1 %>%
   ggplot(aes(x = iteration ,y = coefs,))+
   geom_ribbon(aes(ymax = ci.ub, ymin = ci.lb, x = iteration), fill = "grey70")+
   geom_line()+
   facet_grid(cols = vars(mods))

>>>>

```
```{r coef_iteration}
dat1 %>%
   ggplot(aes(x = iteration ,y = coefs,))+
   geom_ribbon(aes(ymax = ci.ub, ymin = ci.lb, x = iteration), fill = "grey70")+
   geom_line()+
   facet_grid(cols = vars(mods))

```{r pval_iteration}
dat1 %>%
   ggplot(aes(x = iteration ,y = pval,))+
   geom_line()+
   geom_hline(yintercept = 0.05, colour = "grey50", linetype = 2)+
   facet_grid(cols = vars(mods))
